Copies/mL

### 2023-02-03 code/analysis_code/exploratory_daily.qmd
Added Exploratory dust qmd

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "clean_data_date.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

>>>>

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "clean_copies_date.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

### 2023-02-03 code/analysis_code/exploratory_monthly.qmd
Added Exploratory dust qmd

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "clean_data_date.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

>>>>

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "clean_data_copies.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

### 2023-02-03 code/processing_code/copies_calculator.qmd
Added Exploratory dust qmd

Save as RDS and CSV
```{r}
saveRDS(copies_final, file= here("data","processed_data","clean_data.rds"))
write.csv(copies_final,file= here("data","processed_data","clean_data.csv"))

>>>>

Save as RDS and CSV
```{r}
saveRDS(copies_final, file= here("data","processed_data","clean_copies.rds"))
write.csv(copies_final,file= here("data","processed_data","clean_copies.csv"))
